Numerical trajectory patterns of floating macroalgae

### 2020-12-14 thesis_chapter_3.Rmd
deleted mean traj syntax and added to heatmaps. html updated

@@

The model is based on parameterisations that have been used for previous studies investigating iceberg, capsized marine vessels and microplastics. It should be noted that most of the previous studies regarding macroalgae trajectory have investigated rafts and not solitary floating individuals. A kelp raft will vary in size and can range from a few meters across to large dense mats the size of a sports field. Furthermore, some authors suggest that most macroalgae become entangled through ocean currents and not through the hydrodynamic forces that dislodge them. In addition, large kelp rafts are not a characteristics around the coast of the Cape Peninsula but rather solitary kelp are (Pers. Obs). Therefore, the trajectory of solitary *E. maxima* individuals will be considered. Previous studies have made the assumption that floating macroalage move with the same velocity as the ocean current, and instead model a ensemble of particles which trajectories are determined by a combination of ocean currents and/or the effects of winds on currents.

@@

In order to incorporate hydrodynamic and wind drag, the cross-sectional area of the kelp was calculated first. Known geometric shapes reflecting the relevant plant sections were used to estimate the surface area for various parts of the plant, for details please see image/table ???. The dimensional data needed was estimated in cases were data was not available for that particular morphological characteristic. The bulb/pneumatocyst is a highly variable morphological characteristic and in some cases can appear absent, the same is true for the holdfast. Therefore, the cross-sectional area of the bulb/pneumatocyst was not considered in the calculation of overall cross-sectional area. In terms of the holdfast, a standard cross-sectional area was used for simulations where the inclusion of the holdfast was considered. The cross-sectional area calculated was site specific and the dimensions needed were garnered from morphology data from a previous study [@coppin2020]. The minimum, maximum and mean were calculated for each morphological characteristic (see appendix), which were used for calculating the overall minimum, maximum and mean cross-sectional areas needed to run the various simulations. The trajectory of these "types" of cross-sectional areas (minimum, maximum and mean overall cross-sectional area) were used to determine the influence of drag, both hydrodynamic and wind, on overall trajectory.

@@

The use of a spherical shape coefficient was used in the approach to simulate the trajectory of solitary floating *E. maxima*. The drag coefficient for a spherical particle was used in the calculation of hydrodynamic drag as the trajectory model assumes the particles are spherical. The cross-sectional area for each of each virtual plant was converted to the equivalent cross-sectional area for that of a sphere in the equation for calculating hydrodynamic drag: $ F_d = 0.5 \rho A_c C_d U^2$. Since drag force is dependent on the velocity vectors which vary with time, the meridonal and zonal velocities were interpolated and used in the drag force calculation for each time-step. A similar approach was used for the wind drag force. The same equation that was used to calculate hydrodynamic drag, was used to calculate the wind drag the virtual particle. Instead of estimating an ad hoc percentage of wind drag, the wind velocity vectors were interpolated for each time-step and were used in the overall calculation for wind drag force.

To test the different magnitudes that hydrodynamic and wind drag might play in the overall trajectory, simulations were run with varying degrees of drag exposure scenarios. These scenarios were meant to act as proxy for bouyancy, which determines the surface area exposed to hydrodynamic and wind drag. These estimates were expressed as percentages which were used to calculate hydrodynamic and wind drag for applicable simulation. For example, if 80% of the plant is submerged and 20% of above water, then the overall hydrodynamic and wind drag forces would be 80% and 20% of the total drag forces respectively. The exposure scenarios used in this study were 100%, 95%, 90%, and 85% for water drag; 0 %, 5%, 10%, and 15% for wind.

In order to determine the influence of morphology on drag components, simulations were performed for the minimum, mean and maximum cross-sectional areas for one site on the Atlantic side and one site within False Bay (see figure \ref{fig:map})

@@

heatmap_Min_Kfloat_H100_W00 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_EE, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Min_Kfloat_H100_W00, bins = 80, aes(x = lon, y = lat)) +  scale_fill_continuous(type = "viridis", limits = c(1, 13000)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

heatmap_Min_Kfloat_H095_W05 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_EE, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Min_Kfloat_H095_W05, bins = 80, aes(x = lon, y = lat)) +  scale_fill_continuous(type = "viridis", limits = c(1, 13000)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

heatmap_Min_Kfloat_H090_W10 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_EE, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Min_Kfloat_H090_W10, bins = 80, aes(x = lon, y = lat)) +  scale_fill_continuous(type = "viridis", limits = c(1, 13000)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

heatmap_Min_Kfloat_H085_W15 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_EE, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Min_Kfloat_H085_W15, bins = 80, aes(x = lon, y = lat)) +  scale_fill_continuous(type = "viridis", limits = c(1, 13000)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

heatmap_Mean_Kfloat_H100_W00 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_EE, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Mean_Kfloat_H100_W00, bins = 80, aes(x = lon, y = lat)) +  scale_fill_continuous(type = "viridis", limits = c(1, 13000)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

heatmap_Mean_KFloat_H095_W05 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = k_app1, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Mean_KFloat_H095_W05, bins = 80, aes(x = lon, y = lat)) +  scale_fill_continuous(type = "viridis", limits = c(1, 13000)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

heatmap_Mean_KFloat_H090_W10 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = k_app2, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Mean_KFloat_H090_W10, bins = 80, aes(x = lon, y = lat)) +
  scale_fill_continuous(type = "viridis", limits = c(1, 13000)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

heatmap_Mean_KFloat_H085_W15 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = k_app2, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Mean_KFloat_H085_W15, bins = 80, aes(x = lon, y = lat)) +
  scale_fill_continuous(type = "viridis", limits = c(1, 13000)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

heatmap_Max_KFloat_H100_W00 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = k_app2, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Max_Kfloat_H100_W00, bins = 80, aes(x = lon, y = lat)) +
  scale_fill_continuous(type = "viridis", limits = c(1, 13000)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

heatmap_Max_KFloat_H095_W05 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = k_app2, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Max_Kfloat_H095_W05, bins = 80, aes(x = lon, y = lat)) +
  scale_fill_continuous(type = "viridis", limits = c(1, 13000)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

heatmap_Max_KFloat_H090_W10 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = k_app2, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Max_Kfloat_H090_W10, bins = 80, aes(x = lon, y = lat)) +
  scale_fill_continuous(type = "viridis", limits = c(1, 13000)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

heatmap_Max_KFloat_H085_W15 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = k_app2, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Max_Kfloat_H085_W15, bins = 80, aes(x = lon, y = lat)) +
  scale_fill_continuous(type = "viridis", limits = c(1, 13000)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

@@

a <- ggarrange(heatmap_Min_Kfloat_H100_W00, heatmap_Min_Kfloat_H095_W05,heatmap_Min_Kfloat_H090_W10,heatmap_Min_Kfloat_H085_W15, heatmap_Mean_Kfloat_H100_W00, heatmap_Mean_KFloat_H095_W05, heatmap_Mean_KFloat_H090_W10, heatmap_Mean_KFloat_H085_W15, heatmap_Max_KFloat_H100_W00,heatmap_Max_KFloat_H095_W05, heatmap_Max_KFloat_H090_W10, heatmap_Max_KFloat_H085_W15 , labels = c("AUTO"), common.legend = TRUE, legend = c("none"))

ggarrange(heatmap_RK4, a, common.legend = TRUE, legend = c("right"), ncol = 1, nrow = 2)

```{r path plots, warning=FALSE, message=FALSE, echo=FALSE, include=TRUE}

min_area_path <- ggplot() + 
  geom_path(data = Min_Kfloat_H100_W00_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  geom_path(data = Min_Kfloat_H095_W05_mean,aes(x = lon, y = lat, color = 'blue'), show.legend = FALSE) +
  geom_path(data = Min_Kfloat_H090_W10_mean,aes(x = lon, y = lat, color = 'yellow'), show.legend = FALSE) +
  geom_path(data = Min_Kfloat_H085_W15_mean,aes(x = lon, y = lat, color = 'pink'), show.legend = FALSE) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  ggtitle("Minimum cross-sectional area") + 
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

mean_area_path <- ggplot() + 
  geom_path(data = Mean_Kfloat_H100_W00_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  geom_path(data = Mean_KFloat_H095_W05_mean,aes(x = lon, y = lat, color = 'blue'), show.legend = FALSE) +
  geom_path(data = Mean_KFloat_H090_W10_mean,aes(x = lon, y = lat, color = 'yellow'), show.legend = FALSE) +
  geom_path(data = Mean_KFloat_H085_W15_mean,aes(x = lon, y = lat, color = 'pink'), show.legend = FALSE) +
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  ggtitle("Mean cross-sectional area") + 
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

max_area_path <- ggplot() + 
  geom_path(data = Max_Kfloat_H100_W00_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  geom_path(data = Max_Kfloat_H095_W05_mean,aes(x = lon, y = lat, color = 'blue'), show.legend = FALSE) +
  geom_path(data = Max_Kfloat_H090_W10_mean,aes(x = lon, y = lat, color = 'yellow'), show.legend = FALSE) +
  geom_path(data = Max_Kfloat_H085_W15_mean,aes(x = lon, y = lat, color = 'pink'), show.legend = FALSE) +
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  ggtitle("Maximum cross-sectional area") + 
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

ggarrange(min_area_path, mean_area_path, max_area_path, labels = "AUTO")

```{r trajectory plots, echo=FALSE, message=FALSE, warning=FALSE}

>>>>

The model is based on parameterisations that have been used for previous studies investigating iceberg, capsized marine vessels and microplastics. It should be noted that most of the previous studies regarding macroalgae trajectory have investigated rafts and not solitary floating individuals. A kelp raft will vary in size and can range from a few meters across to large dense mats the size of a sports field. Furthermore, some authors suggest that most macroalgae become entangled through ocean currents and not through the hydrodynamic forces that dislodge them. In addition, large kelp rafts are not a characteristics around the coast of the Cape Peninsula but rather solitary kelp are (Pers. Obs). Therefore, the trajectory of only olitary *E. maxima* individuals will be considered. Previous studies have made the assumption that floating macroalage move with the same velocity as the ocean current, and instead model a ensemble of particles which trajectories are determined by a combination of ocean currents and/or the effects of winds on currents.

@@

Virtual particles were released with drag or wind effects from the study site in order to act as a basis for comparison to simulations with varying degrees of hydrodynamic and wind drag. All simulations has the same release location and run for 30 days with hourly outputs using a fourth order Runge-Kutte advection scheme. Brownian motion was also incorporated in order to account for any stochasticity not resolved by the model. These are standard practices for Lagrangian trajectory studies. In order to determine the influence of cross-sectional area on drag components, simulations were performed for the minimum, mean and maximum cross-sectional areas for Kommetjie kelp forest population (see figure \ref{fig:map}). In order to determine the direct effect of wind on trajectory, simulations were run for varying magnitudes of wind exposure for each type of cross-sectional area.

@@

In order to incorporate hydrodynamic and wind drag, the cross-sectional area of the kelp was calculated first. Known geometric shapes reflecting the relevant plant sections were used to estimate the surface area for various parts of the plant, for details please see image/table ???. The dimensional data needed was estimated in cases were data was not available for that particular morphological characteristic. The bulb/pneumatocyst is a highly variable morphological characteristic and in some cases can appear absent, the same is true for the holdfast. Therefore, the cross-sectional area of the bulb/pneumatocyst was not considered in the calculation of overall cross-sectional area. In terms of the holdfast, a standard cross-sectional area was used for simulations where the inclusion of the holdfast was considered. The cross-sectional area calculated was site specific and the dimensions needed were garnered from morphology data from a previous study [@coppin2020]. The minimum, mean and maximum were calculated for each morphological characteristic (see appendix), which were used for calculating the overall minimum, mean and maximum cross-sectional areas needed to run the various simulations. The trajectory of these "types" of cross-sectional areas (minimum, mean and maximum overall cross-sectional area) were used to determine the influence of drag, both hydrodynamic and wind, on overall trajectory.

@@

The use of a spherical shape coefficient was used in the approach to simulate the trajectory of solitary floating *E. maxima*. The drag coefficient for a spherical particle was used in the calculation of hydrodynamic drag as the trajectory model assumes the particles are spherical. The cross-sectional area for each of each virtual plant was converted to the equivalent cross-sectional area for that of a sphere in the equation for calculating hydrodynamic drag: $F_d = 0.5 \rho A_c C_d U^2$, where $\rho$ is the density of seawater or air, $A_c$ is the cross-sectional area exposed to water or wind drag, $C_d$ is the drag coefficient for a spherical particle and $U$ is the surface velocity vector of the flow-/wind- field. Water and wind drag components were calculated separately for both the meridonal and zonal velocity vectors. Since drag force is dependent on the velocity vectors which vary with time, the meridonal and zonal velocities were interpolated and used in the drag force calculation for each time-step. A similar approach was used for the wind drag force. The same equation that was used to calculate hydrodynamic drag, was used to calculate the wind drag the virtual particle.

To test the different magnitudes that hydrodynamic and wind drag might play in the overall trajectory, simulations were run with varying degrees of drag exposure scenarios. These scenarios were meant to act as proxy for buoyancy, which determines the surface area exposed to hydrodynamic and wind drag. These estimates were expressed as percentages which were used to calculate hydrodynamic and wind drag for applicable simulation. For example, if 80% of the plant is submerged and 20% of above water, then the overall hydrodynamic and wind drag forces would be 80% and 20% of the total drag forces respectively. The exposure scenarios used in this study were 100%, 95%, 90%, and 85% for water drag; 0 %, 5%, 10%, and 15% for wind.

@@

heatmap_Min_Kfloat_H100_W00 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_EE, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Min_Kfloat_H100_W00, bins = 80, aes(x = lon, y = lat)) +  scale_fill_continuous(type = "viridis",        limits = c(1, 13000)) +
  geom_path(data = Min_Kfloat_H100_W00_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

heatmap_Min_Kfloat_H095_W05 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_EE, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Min_Kfloat_H095_W05, bins = 80, aes(x = lon, y = lat)) +  scale_fill_continuous(type = "viridis",        limits = c(1, 13000)) +
  geom_path(data = Min_Kfloat_H095_W05_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

heatmap_Min_Kfloat_H090_W10 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_EE, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Min_Kfloat_H090_W10, bins = 80, aes(x = lon, y = lat)) +  scale_fill_continuous(type = "viridis",        limits = c(1, 13000)) +
  geom_path(data = Min_Kfloat_H090_W10_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

heatmap_Min_Kfloat_H085_W15 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_EE, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Min_Kfloat_H085_W15, bins = 80, aes(x = lon, y = lat)) +  scale_fill_continuous(type = "viridis",        limits = c(1, 13000)) +
  geom_path(data = Min_Kfloat_H085_W15_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

heatmap_Mean_Kfloat_H100_W00 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_EE, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Mean_Kfloat_H100_W00, bins = 80, aes(x = lon, y = lat)) +  scale_fill_continuous(type = "viridis",       limits = c(1, 13000)) +
  geom_path(data = Mean_Kfloat_H100_W00_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

heatmap_Mean_KFloat_H095_W05 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = k_app1, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Mean_KFloat_H095_W05, bins = 80, aes(x = lon, y = lat)) +  scale_fill_continuous(type = "viridis",       limits = c(1, 13000)) +
  geom_path(data = Mean_KFloat_H095_W05_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

heatmap_Mean_KFloat_H090_W10 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = k_app2, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Mean_KFloat_H090_W10, bins = 80, aes(x = lon, y = lat)) +
  scale_fill_continuous(type = "viridis", limits = c(1, 13000)) +
  geom_path(data = Mean_KFloat_H090_W10_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

heatmap_Mean_KFloat_H085_W15 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = k_app2, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Mean_KFloat_H085_W15, bins = 80, aes(x = lon, y = lat)) +
  scale_fill_continuous(type = "viridis", limits = c(1, 13000)) +
  geom_path(data = Mean_KFloat_H085_W15_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

heatmap_Max_KFloat_H100_W00 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = k_app2, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Max_Kfloat_H100_W00, bins = 80, aes(x = lon, y = lat)) +
  scale_fill_continuous(type = "viridis", limits = c(1, 13000)) +
  geom_path(data = Max_Kfloat_H100_W00_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

heatmap_Max_KFloat_H095_W05 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = k_app2, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Max_Kfloat_H095_W05, bins = 80, aes(x = lon, y = lat)) +
  scale_fill_continuous(type = "viridis", limits = c(1, 13000)) +
  geom_path(data = Max_Kfloat_H095_W05_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

heatmap_Max_KFloat_H090_W10 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = k_app2, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Max_Kfloat_H090_W10, bins = 80, aes(x = lon, y = lat)) +
  scale_fill_continuous(type = "viridis", limits = c(1, 13000)) +
  geom_path(data = Max_Kfloat_H090_W10_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

heatmap_Max_KFloat_H085_W15 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = k_app2, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Max_Kfloat_H085_W15, bins = 80, aes(x = lon, y = lat)) +
  scale_fill_continuous(type = "viridis", limits = c(1, 13000)) +
  geom_path(data = Max_Kfloat_H085_W15_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

@@

ggarrange(heatmap_Min_Kfloat_H100_W00, heatmap_Min_Kfloat_H095_W05,heatmap_Min_Kfloat_H090_W10,heatmap_Min_Kfloat_H085_W15, heatmap_Mean_Kfloat_H100_W00, heatmap_Mean_KFloat_H095_W05, heatmap_Mean_KFloat_H090_W10, heatmap_Mean_KFloat_H085_W15, heatmap_Max_KFloat_H100_W00,heatmap_Max_KFloat_H095_W05, heatmap_Max_KFloat_H090_W10, heatmap_Max_KFloat_H085_W15 , labels = c("AUTO"), common.legend = TRUE, legend = c("none"))

#ggarrange(heatmap_RK4, a, common.legend = TRUE, legend = c("right"), ncol = 1, nrow = 2)

```
```{r trajectory plots, echo=FALSE, message=FALSE, warning=FALSE}
